
Importing the dataset
```{r}
data <- read.csv("C:\\Users\\HP\\Desktop\\DS HA\\SYB64_263_202110_Production, Trade and Supply of Energy (2).csv", header = TRUE)
head(data)
```

Converting string values of 'value' to integer by removing ','

```{r}
data$Value <- as.numeric(gsub(",","",data$Value))
```

Importing library ggplot2

```{r}
library(ggplot2)
```

Importing a new dataset consisting of only 'Primary energy production (petajoules)' values

This data set has only the 5 countries which we are comparing - 
1. India
2. United Kingdom
3. United States of America
4. Italy
5. Israel


```{r}
data_primary <- read.csv("C:\\Users\\HP\\Desktop\\DS HA\\Primary_Energy.xlsx.csv", header = TRUE)
head(data_primary)
```

Performing the same data cleaning steps

```{r}
data_primary$Value <- as.numeric(gsub(",","",data_primary$Value))
```

Visualizing a grouped bar plot to compare these values

```{r}
ggplot(data_primary, aes(fill=ï..Country.Region, y=Value, x=Year)) + 
    geom_bar(position="dodge", stat="identity") + theme(axis.text.x =element_text(angle=90,vjust=0.5),plot.title=element_text(color="black",size=16,face="italic"))+labs(x="",y="Value",title="Primary Production of 5 countries")
```

After comparing Primary....

```{r}
data_imports <- read.csv("C:\\users\\HP\\Desktop\\DS HA\\Dataset_NetImports.csv", header = TRUE)
head(data)
```
```{r}
data_imports$Value <- as.numeric(gsub(",","",data_imports$Value))

```

```{r}
ggplot(data_imports, aes(fill=Country.Region, y=Value, x=Year)) + 
    geom_bar(position="dodge", stat="identity") + theme(axis.text.x =element_text(angle=90,vjust=0.5),plot.title=element_text(color="black",size=16,face="italic"))+labs(x="",y="Value",title="Net Imports of 5 countries")
```

```{r}
data_total_supply <- read.csv("C:\\users\\HP\\Desktop\\DS HA\\totalSupply.csv", header = TRUE)
head(data_total_supply)
```

```{r}
data_total_supply$Value <- as.numeric(gsub(",","",data_total_supply$Value))

```

```{r}
ggplot(data_total_supply, aes(fill=ï..Country.Region, y=Value, x=Year)) + 
    geom_bar(position="dodge", stat="identity") + theme(axis.text.x =element_text(angle=90,vjust=0.5),plot.title=element_text(color="black",size=16,face="italic"))+labs(x="",y="Value",title="Total Supply of 5 countries")
```

```{r}
data_stocks <- read.csv("C:\\users\\HP\\Desktop\\DS HA\\stocks.csv", header = TRUE)
head(data_stocks)
```

```{r}
data_stocks$Value <- as.numeric(gsub(",","",data_stocks$Value))

```

```{r}
ggplot(data_stocks, aes(fill=ï..Country.Region, y=Value, x=Year)) + 
    geom_bar(position="dodge", stat="identity") + theme(axis.text.x =element_text(angle=90,vjust=0.5),plot.title=element_text(color="black",size=16,face="italic"))+labs(x="",y="Value",title="Change in stocks of 5 countries")
```

```{r}
data_supply_pc <- read.csv("C:\\users\\HP\\Desktop\\DS HA\\Supply_per_capita.csv", header = TRUE)
head(data_supply_pc)
```
```{r}
data_supply_pc$Value <- as.numeric(gsub(",","",data_supply_pc$Value))

```

```{r}
ggplot(data_supply_pc, aes(fill=Country.Region, y=Value, x=Year)) + 
    geom_bar(position="dodge", stat="identity") + theme(axis.text.x =element_text(angle=90,vjust=0.5),plot.title=element_text(color="black",size=16,face="italic"))+labs(x="",y="Value",title="Supply per capita of 5 countries")
```
```{r}
library(ggplot2)
theme_set(theme_classic())
```


```{r}
data_total_supply_box <- read.csv("C:\\Users\\HP\\Desktop\\DS HA\\totalSupply.csv", header = TRUE)
head(data_total_supply_box)
```


```{r}
library(ggplot2)
library(dplyr)
glimpse(data_supply_pc)
box <- ggplot(data_supply_pc,aes(x=Country.Region
,y=Value))
box + geom_boxplot()

box +
    geom_boxplot(outlier.colour = "red",
        outlier.shape = 2,
        outlier.size = 3) +
    theme_classic()

box +
    geom_boxplot() +
    stat_summary(fun.y = mean,
        geom = "point",
        size = 3,
        color = "steelblue") +
    theme_classic()

box +
    geom_boxplot() +
    geom_dotplot(binaxis = 'y',
        dotsize = 1,
        stackdir = 'center') +
    theme_classic()

ggplot(data_supply_pc, aes(x = Country.Region, y = Value, color = Country.Region)) +
    geom_boxplot() +
    theme_classic()
```

